---
title: "Predicting House Pricing"
author: "Rahul Singh"
date: "1/23/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls()) #to remove previously existing data in the R memory
library(purrr)
library(visdat)
library(dplyr)
library(ggplot2)
library(plyr)
library(moments)
library(glmnet)
library(caret)
library(FSelector) #<- lots of problems with this package!
```


```{r}
rm(list=ls()) #to remove previously existing data in the R memory
training_data<-read.csv("~/Desktop/IE MBD Term2/Machine Learning 2/CODES/Practice 1/House Pricing Kaggle/train.csv") #importing training data
test_data<-read.csv("~/Desktop/IE MBD Term2/Machine Learning 2/CODES/Practice 1/House Pricing Kaggle/test.csv") #importing testing data
```

For detecting duplicate values
```{r}
length(unique(training_data$Id)) == nrow(training_data) #returns TRUE, no duplicates present
training_data[duplicated(training_data),] #returns 0 rows are duplicates
```



For observing missing values
```{r}
map_df(training_data, function(x) sum(is.na(x))) #to see if there are any NA or missing values in data
vis_miss(training_data) #to visualize missing values
```

Removing id column in data frame as it is not needed in prediction
```{r}
training_data<- training_data %>% dplyr::select(-Id)
```

Hunting NAs
```{r NAs discovery}
na.cols <- which(colSums(is.na(training_data)) > 0)
sort(colSums(sapply(training_data[na.cols], is.na)), decreasing = TRUE)
paste('There are', length(na.cols), 'columns with missing values')
```

```{r Train NA Imputation}
# Alley : NA means "no alley access"
training_data$Alley = factor(training_data$Alley, levels=c(levels(training_data$Alley), "None"))
training_data$Alley[is.na(training_data$Alley)] = "None" #replacing NA with 'none'

training_data$BedroomAbvGr[is.na(training_data$BedroomAbvGr)] <- 0 #wherever BedroomAbvGr is NA, it is set to 0

# Bsmt : NA for basement features is "no basement"
training_data$BsmtQual = factor(training_data$BsmtQual, levels=c(levels(training_data$BsmtQual), "No"))
training_data$BsmtQual[is.na(training_data$BsmtQual)] = "No" #replaces NA with 'No'

training_data$BsmtCond = factor(training_data$BsmtCond, levels=c(levels(training_data$BsmtCond), "No"))
training_data$BsmtCond[is.na(training_data$BsmtCond)] = "No" #replaces NA with 'No'

training_data$BsmtExposure[is.na(training_data$BsmtExposure)] = "No" #replaces NA with 'No'

training_data$BsmtFinType1 = factor(training_data$BsmtFinType1, levels=c(levels(training_data$BsmtFinType1), "No"))
training_data$BsmtFinType1[is.na(training_data$BsmtFinType1)] = "No" #replaces NA with 'No'

training_data$BsmtFinType2 = factor(training_data$BsmtFinType2, levels=c(levels(training_data$BsmtFinType2), "No"))
training_data$BsmtFinType2[is.na(training_data$BsmtFinType2)] = "No" #replaces NA with 'No'

# Fence : NA means "no fence"
training_data$Fence = factor(training_data$Fence, levels=c(levels(training_data$Fence), "No"))
training_data$Fence[is.na(training_data$Fence)] = "No" #replaces NA with 'No'

# FireplaceQu : NA means "no fireplace"
training_data$FireplaceQu = factor(training_data$FireplaceQu, levels=c(levels(training_data$FireplaceQu), "No"))
training_data$FireplaceQu[is.na(training_data$FireplaceQu)] = "No" #replaces NA with 'No'

# Garage : NA for garage features is "no garage"
training_data$GarageType = factor(training_data$GarageType, levels=c(levels(training_data$GarageType), "No"))
training_data$GarageType[is.na(training_data$GarageType)] = "No" #replaces NA with 'No'

training_data$GarageFinish = factor(training_data$GarageFinish, levels=c(levels(training_data$GarageFinish), "No"))
training_data$GarageFinish[is.na(training_data$GarageFinish)] = "No" #replaces NA with 'No'

training_data$GarageQual = factor(training_data$GarageQual, levels=c(levels(training_data$GarageQual), "No"))
training_data$GarageQual[is.na(training_data$GarageQual)] = "No" #replaces NA with 'No'

training_data$GarageCond = factor(training_data$GarageCond, levels=c(levels(training_data$GarageCond), "No"))
training_data$GarageCond[is.na(training_data$GarageCond)] = "No" #replaces NA with 'No'

# LotFrontage : NA most likely means no lot frontage
training_data$LotFrontage[is.na(training_data$LotFrontage)] <- 0 #replaces NA with 0

# MasVnrType : NA most likely means no veneer
training_data$MasVnrType[is.na(training_data$MasVnrType)] = "None"
training_data$MasVnrArea[is.na(training_data$MasVnrArea)] <- 0 #replaces NA with 0

# MiscFeature : NA = "no misc feature"
training_data$MiscFeature = factor(training_data$MiscFeature, levels=c(levels(training_data$MiscFeature), "No"))
training_data$MiscFeature[is.na(training_data$MiscFeature)] = "No" #replaces NA with 'No'

# PoolQC : data description says NA means "no pool"
training_data$PoolQC = factor(training_data$PoolQC, levels=c(levels(training_data$PoolQC), "No"))
training_data$PoolQC[is.na(training_data$PoolQC)] = "No" #replaces NA with 'No'

# Electrical : NA means "UNK"
training_data$Electrical = factor(training_data$Electrical, levels=c(levels(training_data$Electrical), "UNK"))
training_data$Electrical[is.na(training_data$Electrical)] = "UNK" #replaces NA with 'UNK'

# GarageYrBlt: It seems reasonable that most houses would build a garage when the house itself was built.
idx <- which(is.na(training_data$GarageYrBlt))
training_data[idx, 'GarageYrBlt'] <- training_data[idx, 'YearBuilt'] #replaces the na values with YrBuilt

na.cols <- which(colSums(is.na(training_data)) > 0)
paste('There are now', length(na.cols), 'columns with missing values')
```

We repeat the process for test_data
```{r Test Inputation}
# Alley : data description says NA means "no alley access"
test_data$Alley = factor(test_data$Alley, levels=c(levels(test_data$Alley), "None"))
test_data$Alley[is.na(test_data$Alley)] = "None"

test_data$BedroomAbvGr[is.na(test_data$BedroomAbvGr)] <- 0

# BsmtQual etc : data description says NA for basement features is "no basement"
test_data$BsmtQual = factor(test_data$BsmtQual, levels=c(levels(test_data$BsmtQual), "No"))
test_data$BsmtQual[is.na(test_data$BsmtQual)] = "No"

test_data$BsmtCond = factor(test_data$BsmtCond, levels=c(levels(test_data$BsmtCond), "No"))
test_data$BsmtCond[is.na(test_data$BsmtCond)] = "No"

test_data$BsmtExposure[is.na(test_data$BsmtExposure)] = "No"

test_data$BsmtFinType1 = factor(test_data$BsmtFinType1, levels=c(levels(test_data$BsmtFinType1), "No"))
test_data$BsmtFinType1[is.na(test_data$BsmtFinType1)] = "No"

test_data$BsmtFinType2 = factor(test_data$BsmtFinType2, levels=c(levels(test_data$BsmtFinType2), "No"))
test_data$BsmtFinType2[is.na(test_data$BsmtFinType2)] = "No"

# Fence : data description says NA means "no fence"
test_data$Fence = factor(test_data$Fence, levels=c(levels(test_data$Fence), "No"))
test_data$Fence[is.na(test_data$Fence)] = "No"

# FireplaceQu : data description says NA means "no fireplace"
test_data$FireplaceQu = factor(test_data$FireplaceQu, levels=c(levels(test_data$FireplaceQu), "No"))
test_data$FireplaceQu[is.na(test_data$FireplaceQu)] = "No"

# GarageType etc : data description says NA for garage features is "no garage"
test_data$GarageType = factor(test_data$GarageType, levels=c(levels(test_data$GarageType), "No"))
test_data$GarageType[is.na(test_data$GarageType)] = "No"

test_data$GarageFinish = factor(test_data$GarageFinish, levels=c(levels(test_data$GarageFinish), "No"))
test_data$GarageFinish[is.na(test_data$GarageFinish)] = "No"

test_data$GarageQual = factor(test_data$GarageQual, levels=c(levels(test_data$GarageQual), "No"))
test_data$GarageQual[is.na(test_data$GarageQual)] = "No"

test_data$GarageCond = factor(test_data$GarageCond, levels=c(levels(test_data$GarageCond), "No"))
test_data$GarageCond[is.na(test_data$GarageCond)] = "No"

# LotFrontage : NA most likely means no lot frontage
test_data$LotFrontage[is.na(test_data$LotFrontage)] <- 0

# MasVnrType : NA most likely means no veneer
test_data$MasVnrType[is.na(test_data$MasVnrType)] = "None"
test_data$MasVnrArea[is.na(test_data$MasVnrArea)] <- 0

# MiscFeature : data description says NA means "no misc feature"
test_data$MiscFeature = factor(test_data$MiscFeature, levels=c(levels(test_data$MiscFeature), "No"))
test_data$MiscFeature[is.na(test_data$MiscFeature)] = "No"

# PoolQC : data description says NA means "no pool"
test_data$PoolQC = factor(test_data$PoolQC, levels=c(levels(test_data$PoolQC), "No"))
test_data$PoolQC[is.na(test_data$PoolQC)] = "No"

```


## Factorize features
Some numerical features are actually really categories

```{r Factorize features}

training_data$MSSubClass <- as.factor(training_data$MSSubClass) #converting from int to factor
training_data$MoSold <- as.factor(training_data$MoSold) #converting from int to factor

test_data$MSSubClass <- as.factor(test_data$MSSubClass) #converting from int to factor
test_data$MoSold <- as.factor(test_data$MoSold) #converting from int to factor
```


## Skewness
Skewness in the Target value
```{r}
#log transformation removes skewness
# get data frame of SalePrice and log(SalePrice + 1) for plotting
df <- rbind(data.frame(version="log(price+1)",x=log(training_data$SalePrice + 1)),
            data.frame(version="price",x=training_data$SalePrice))

ggplot(data=df) +
  facet_wrap(~version,ncol=2,scales="free_x") +
  geom_histogram(aes(x=x), bins = 50)
```


We therefore transform the target value applying log
```{r Log transform the target for official scoring}
# Log transform the target for official scoring
training_data$SalePrice <- log1p(training_data$SalePrice)
```


The same "skewness" observed in the target variable also affects other variables. To facilitate the application of the regression model we are going to also eliminate this skewness
For numeric feature with excessive skewness, perform log transformation
```{r}

column_types <- sapply(names(training_data),function(x){class(training_data[[x]])})
numeric_columns <-names(column_types[column_types != "factor"])

# skew of each variable
skew <- sapply(numeric_columns,function(x){skewness(training_data[[x]],na.rm = T)})

# transform all variables above a threshold skewness.
skew <- skew[skew > 0.75]
for(x in names(skew)) {
  training_data[[x]] <- log(training_data[[x]] + 1)
}
```

The same for the test data
```{r}
column_types <- sapply(names(test_data),function(x){class(test_data[[x]])})
numeric_columns <-names(column_types[column_types != "factor"])

skew <- sapply(numeric_columns,function(x){skewness(test_data[[x]],na.rm = T)})
skew <- skew[skew > 0.75]
for(x in names(skew)) {
  test_data[[x]] <- log(test_data[[x]] + 1)
}
```

## Train, Validation Spliting
We are going to split the annotated dataset in training and validation for the later evaluation of our regression models
```{r Train test split}
# I found this function, that is worth to save for future ocasions.
splitdf <- function(dataframe, seed=NULL) {
  if (!is.null(seed)) set.seed(seed)
 	index <- 1:nrow(dataframe)
 	trainindex <- sample(index, trunc(length(index)/1.5))
 	trainset <- dataframe[trainindex, ]
 	testset <- dataframe[-trainindex, ]
 	list(trainset=trainset,testset=testset)
}
splits <- splitdf(training_data, seed=1)
training <- splits$trainset
validation <- splits$testset
#the function which was created above splits the dataset into training and validation
```

If we inspect in detail the categorical variables of the dataset, we'll see that some are incomplete: they only have a unique value for all the dataset.
These features are not valuable. Three important aspects that a feature should have: informative, <b>discriminative</b> and independent. Incomplete cases are not discriminative at all.
In addition, this might create problems when fitting the regression model

The following code show the incomplete cases
```{r}
## remove incomplete cases
paste("Training set incomplete cases")
sapply(lapply(na.omit(training)[sapply(na.omit(training), is.factor)], droplevels), nlevels)
#The function droplevels is used to drop unused levels from a factor or, more commonly, from factors in a data frame
paste("Validation set incomplete cases")
sapply(lapply(na.omit(validation)[sapply(na.omit(validation), is.factor)], droplevels), nlevels)
paste("Test set incomplete cases")
sapply(lapply(na.omit(test_data)[sapply(na.omit(test_data), is.factor)], droplevels), nlevels)
```

We remove the detected incomplete cases
```{r}
# Remove the Utilities feature from the dataset (It only has one value)
training <- training[,-which(names(training) == "Utilities")] 
#Utilities column in data has all values called 'AllPub'; so we remove it
validation <- validation[,-which(names(validation) == "Utilities")]
test_data <- test_data[,-which(names(test_data) == "Utilities")]

```

# Feature Engineering
We here start the Feature Engineering.

## Filtering Methods
We will rank the features according to their predictive power according to these methodologies: the Chi Squared Independence test and the Information Gain.

#### Full Model
We must always fit a lm model with all the features to have a baseline to evaluate the impact of the feature engineering.
```{r Full Regression model, message=FALSE, warning=FALSE}

set.seed(121)
train_control_config <- trainControl(method = "repeatedcv", 
                       number = 5, 
                       repeats = 1,
                       returnResamp = "all")

full.lm.mod <- train(SalePrice ~ ., data = training, 
               method = "lm", 
               metric = "RMSE",
               preProc = c("center", "scale"),
               trControl=train_control_config)

for (x in names(validation)) {
  full.lm.mod$xlevels[[x]] <- union(full.lm.mod$xlevels[[x]], levels(validation[[x]]))
}
full.lm.mod.pred <- predict(full.lm.mod, validation[,-ncol(validation)])
full.lm.mod.pred[is.na(full.lm.mod.pred)] <- 0

my_data=as.data.frame(cbind(predicted=full.lm.mod.pred,observed=validation$SalePrice))

ggplot(my_data,aes(predicted,observed))+
  geom_point() + geom_smooth(method = "lm") +
  labs(x="Predicted") +
  ggtitle('Linear Model')

paste("Full Linear Regression RMSE = ", sqrt(mean((full.lm.mod.pred - validation$SalePrice)^2)))
```

### Chi-squared Selection
Making use of the `FSelector` package <https://cran.r-project.org/web/packages/FSelector/FSelector.pdf>, rank the features according to the Chi Squared value. If you've problems with this package (some of us have problems with it), do some research to find another packages that will provide the Chi squared selection.

Does it make sense to remove some features? Is so, do it!
```{r}
weights<- data.frame(chi.squared(SalePrice~., training_data))
weights$feature <- rownames(weights)
weights[order(weights$attr_importance, decreasing = TRUE),]
```
```{r}
chi_squared_features <- weights$feature[weights$attr_importance >= 0.1] #selecting variables with attr_importance more thank 0.1
```


#### Evaluation
Evaluate the impact (in terms of RMSE) of the feature selection.
To that end, execute the previous LM model taking as input the filtered training set
```{r Chi-Squared Regression, message=FALSE, warning=FALSE}
# Compute your model with the new features and compute the new RMSE to decide whether to keep the new variables or not.
chi_squared.lm.mod <- train(SalePrice ~ ., data = training[append(chi_squared_features, "SalePrice")], 
               method = "lm", 
               metric = "RMSE",
               preProc = c("center", "scale"),
               trControl=train_control_config)

for (x in names(validation)) {
  chi_squared.lm.mod$xlevels[[x]] <- union(chi_squared.lm.mod$xlevels[[x]], levels(validation[[x]]))
}
chi_squared.lm.mod.pred <- predict(chi_squared.lm.mod, validation[,-ncol(validation)])
chi_squared.lm.mod.pred[is.na(chi_squared.lm.mod.pred)] <- 0

my_data=as.data.frame(cbind(predicted=chi_squared.lm.mod.pred,observed=validation$SalePrice))

ggplot(my_data,aes(predicted,observed))+
  geom_point() + geom_smooth(method = "lm") +
  labs(x="Predicted") +
  ggtitle('Linear Model')
```

Experiment with diferent cutoffs to filter the features and evaluate their impact in the perfomarnce. Select the cutoff that you consider more appropiate.
```{r}
#onserve how selecting a threshold value of 0.5 actually distorts the regression
chi_squared_features <- weights$feature[weights$attr_importance >= 0.5] #selecting variables with attr_importance more thank 0.4

# Compute your model with the new features and compute the new RMSE to decide whether to keep the new variables or not.
chi_squared.lm.mod <- train(SalePrice ~ ., data = training[append(chi_squared_features, "SalePrice")], 
               method = "lm", 
               metric = "RMSE",
               preProc = c("center", "scale"),
               trControl=train_control_config)

for (x in names(validation)) {
  chi_squared.lm.mod$xlevels[[x]] <- union(chi_squared.lm.mod$xlevels[[x]], levels(validation[[x]]))
}
chi_squared.lm.mod.pred <- predict(chi_squared.lm.mod, validation[,-ncol(validation)])
chi_squared.lm.mod.pred[is.na(chi_squared.lm.mod.pred)] <- 0

my_data=as.data.frame(cbind(predicted=chi_squared.lm.mod.pred,observed=validation$SalePrice))

ggplot(my_data,aes(predicted,observed))+
  geom_point() + geom_smooth(method = "lm") +
  labs(x="Predicted") +
  ggtitle('Linear Model')
```


### Information Gain Selection
Let's experiment now with Information Gain Selection.
Making also use of the `FSelector` package <https://cran.r-project.org/web/packages/FSelector/FSelector.pdf>, rank the features according to their Information Gain and filter those which you consider, according to the IG value. Again, there're more alternatives to compute the IG.
```{r}
weights<- data.frame(information.gain(SalePrice~., training_data))
weights$feature <- rownames(weights)
weights[order(weights$attr_importance, decreasing = TRUE),]

```
```{r}
information_gain_features <- weights$feature[weights$attr_importance >= 0.01] #setting the cut-off to select features
```


#### Evaluation
Evaluate the impact of the IG selection in the model performance
```{r Information Gain Regression Model, message=FALSE, warning=FALSE}
ig.lm.mod <- train(SalePrice ~ ., data = training[append(information_gain_features, "SalePrice")], 
               method = "lm", 
               metric = "RMSE",
               preProc = c("center", "scale"),
               trControl=train_control_config)

for (x in names(validation)) {
  ig.lm.mod$xlevels[[x]] <- union(ig.lm.mod$xlevels[[x]], levels(validation[[x]]))
}
ig.lm.mod.pred <- predict(ig.lm.mod, validation[,-ncol(validation)])
ig.lm.mod.pred[is.na(ig.lm.mod.pred)] <- 0

my_data=as.data.frame(cbind(predicted=ig.lm.mod.pred,observed=validation$SalePrice))

ggplot(my_data,aes(predicted,observed))+
  geom_point() + geom_smooth(method = "lm") +
  labs(x="Predicted") +
  ggtitle('Linear Model')
```

```{r}
paste("IG Filtered Linear Regression RMSE = ", sqrt(mean((ig.lm.mod.pred - validation$SalePrice)^2)))
```

Using the result of the evaluation, filter the dataset (according to the method and cutoff that you decide)

Based on these results, we filter the training and validation set with the Information Gain features.
```{r}
training <- training[append(information_gain_features, "SalePrice")]
validation <- validation[append(information_gain_features, "SalePrice")]
```

## Wrapper Methods
Let us experiment now with Wrapper Methods. In particular, we are going to apply Forward Stepwise Selection Methods to find the best feature combination for this dataset.

### Stepwise

#### Backward Stepwise
Caret package provides a useful and easy way of experimenting with stepwise selection. Try it to know what a wrapper method suggests as the best possible subset of features and compare your results with the baseline.

```{r Backward Stepwise, message=FALSE, warning=FALSE}

train_control_config_4_stepwise <- trainControl(method = "none")

backward.lm.mod <- train(SalePrice ~ ., data = training, 
               method = "glmStepAIC", 
               direction = "backward",
               trace = FALSE,
               metric = "RMSE",
               steps = 15,
               preProc = c("center", "scale"),
               trControl=train_control_config_4_stepwise)

```

Printout only the selected features.
```{r}
paste("Features Selected",backward.lm.mod$finalModel$formula[3])
```

```{r}
# Compute RMSE
for (x in names(validation)) {
  backward.lm.mod$xlevels[[x]] <- union(backward.lm.mod$xlevels[[x]], levels(validation[[x]]))
}
backward.lm.mod.pred <- predict(backward.lm.mod, validation[,-ncol(validation)])
backward.lm.mod.pred[is.na(backward.lm.mod.pred)] <- 0



paste("Forward Linear Regression RMSE = ", sqrt(mean((backward.lm.mod.pred - validation$SalePrice)^2)))

```

```{r}
my_data=as.data.frame(cbind(predicted=backward.lm.mod.pred,observed=validation$SalePrice))
ggplot(my_data,aes(predicted,observed))+
  geom_point() + geom_smooth(method = "lm") +
  labs(x="Predicted") +
  ggtitle('Linear Model')
```



## Embedded
Finally, we will experiment with embedded methods. 
In particular we are going to focus on Ridge and  Lasso Regularization.

### Ridge Regression
For this exercise, we are going to make use of the <a href="https://cran.r-project.org/web/packages/glmnet/index.html">`glmnet`</a> library. Take a look to the library and fit a glmnet model for Ridge Regression, using the grid of lambda values provided.
```{r Ridge Regression, warning=FALSE}
lambdas <- 10^seq(-2, 3, by = .1)
ridge.mod <- glmnet(x = data.matrix(training[,-ncol(training)]), y=training$SalePrice, alpha = 0, lambda = lambdas)
```

#### Evaluation
Plotting the RMSE for the different lambda values, we can see the impact of this parameter in the model performance.
Small values seem to work better for this dataset
```{r Ridge Evaluation}
RMSE = numeric(length(lambdas))
for (i in seq_along(lambdas)){
  ridge.pred=predict(ridge.mod, s=lambdas[i], data.matrix(validation[,-ncol(validation)]))
  RMSE[i] <- sqrt(mean((ridge.pred - validation$SalePrice)^2))
}
plot(lambdas, RMSE, main="Ridge", log="x", type = "b")
```


##### Cross Validation
Making use of cv.glmnet <https://www.rdocumentation.org/packages/glmnet/versions/2.0-12/topics/cv.glmnet>, create a cross-validated Ridge Regression Model for the provided lambdas.

Plotting again the error, CV give us a better understanding on the impact of lambda in the model performance
```{r}
ridge.cv_fit <- cv.glmnet(x = data.matrix(training[,-ncol(training)]), y=training$SalePrice, alpha = 0, lambda = lambdas)
plot(ridge.cv_fit)
```


<b>Interpretation:</b>
 - The plot shows the MSE (red dots) for the provided lambda values (included in the grid).
 - The confidence intervals represent error estimates for the RSE, computed using CV. 
 - The vertical lines show the locations of ??min (lambda that achives the best MSE) and ??1se (the largest ?? value within 1 standard error of ??min. Using ??1se hedges against overfitting by selecting a larger ?? value than the min).
 - The numbers across the top are the number of nonzero coefficient estimates.


Select the best lambda form the CV model, use it to predict the target value of the validation set and evaluate the results (in terms of RMSE)
```{r}
bestlam <- ridge.cv_fit$lambda.min
paste("Best Lambda value from CV=", bestlam)
```

```{r}
ridge.pred=predict(ridge.mod, s=bestlam, data.matrix(validation[,-ncol(validation)]))
paste("RMSE for lambda ", bestlam, " = ", sqrt(mean((ridge.pred - validation$SalePrice)^2)))
```


Predict with that lambda on the validation set
```{r}
lam1se <- ridge.cv_fit$lambda.1se
paste("Lambda 1se value from CV=", lam1se)
```

```{r}
ridge.pred=predict(ridge.mod, s=lam1se, data.matrix(validation[,-ncol(validation)]))
paste("RMSE for lambda ", lam1se, " = ", sqrt(mean((ridge.pred - validation$SalePrice)^2)))
```


As you can see, the result is almost the same, but the 1se value is less prone to overfitting

Let's plot the predictions against the actual values to have an idea of the model performance
```{r}
# Plot important coefficients
my_data=as.data.frame(cbind(predicted=ridge.pred,observed=validation$SalePrice))

ggplot(my_data,aes(my_data["1"],observed))+
  geom_point()+geom_smooth(method="lm")+
  scale_x_continuous(expand = c(0,0)) +
  labs(x="Predicted") +
  ggtitle('Ridge')
```

Rank the variables according to the importance attributed by the model
```{r}
# Print, plot variable importance
imp <- varImp(ridge.mod, lambda = bestlam)
names <- rownames(imp)[order(imp$Overall, decreasing=TRUE)]
importance <- imp[names,]

data.frame(row.names = names, importance)
```

### Lasso Regresion
Using again the <a href="https://cran.r-project.org/web/packages/glmnet/index.html">`glmnet`</a> library, fit a Lasso Regression (take a look to the alpha parameter) using the grid of lambda values provided.


####Evaluation

Plot the RMSE for the different lambda values and Explain the results.


```{r}
lambdas <- 10^seq(-3, 3, by = .1)

lasso.cv_fit <- cv.glmnet(x = data.matrix(training[,-ncol(training)]), y=training$SalePrice, alpha = 1, lambda = lambdas)
plot(lasso.cv_fit)
```
*Interpretation:* In contrast to Ridge Regression, Lasso Regression performs feature selection (it is forcing the coefficients to be 0), as you can see in the top numbers in the plot.

Select the best lambda form the CV model, use it to predict the target value of the validation set and evaluate the results (in terms of RMSE)
```{r}
bestlam <- lasso.cv_fit$lambda.min
paste("Best Lambda value from CV=", bestlam)
```

```{r}
lasso.mod <- glmnet(x = data.matrix(training[,-ncol(training)]), y=training$SalePrice, alpha = 1, lambda = lambdas)
lasso.pred=predict(lasso.mod, s=bestlam, data.matrix(validation[,-ncol(validation)]))
paste("RMSE for lambda ", bestlam, " = ", sqrt(mean((lasso.pred - validation$SalePrice)^2)))
```

Select the λ1se value from the CV model to predict on the validation set
```{r}
lam1se <- lasso.cv_fit$lambda.1se
paste("Lambda 1se value from CV=", lam1se)
```

```{r}
lasso.mod <- glmnet(x = data.matrix(training[,-ncol(training)]), y=training$SalePrice, alpha = 1, lambda = lambdas)
lasso.pred=predict(lasso.mod, s=lam1se, data.matrix(validation[,-ncol(validation)]))
paste("RMSE for lambda ", lam1se, " = ", sqrt(mean((lasso.pred - validation$SalePrice)^2)))
```

Predictions against the actual values
```{r}
# Plot important coefficients
my_data=as.data.frame(cbind(predicted=lasso.pred,observed=validation$SalePrice))

ggplot(my_data,aes(my_data["1"],observed))+
  geom_point()+geom_smooth(method="lm")+
  scale_x_continuous(expand = c(0,0)) +
  labs(x="Predicted") +
  ggtitle('Lasso')
```

Variable importance
```{r}
# Print, plot variable importance
imp <- varImp(lasso.mod, lambda = bestlam)
names <- rownames(imp)[order(imp$Overall, decreasing=TRUE)]
importance <- imp[names,]

data.frame(row.names = names, importance)
```

###Prediction on the test data
```{r}
log_prediction <- predict(lasso.cv_fit, s=lasso.cv_fit$lambda.min, newx =data.matrix(test_data[information_gain_features]))

actual_pred <- exp(log_prediction)-1
hist(actual_pred)
```

```{r}
submit <- data.frame(Id=test_data$Id,SalePrice=actual_pred)
colnames(submit) <-c("Id", "SalePrice")

submit$SalePrice[is.na(submit$SalePrice)] <- 0
replace_value_for_na <- sum(na.omit(submit$SalePrice))/(nrow(submit) - sum(submit$SalePrice == 0))
submit$SalePrice[submit$SalePrice == 0] <- replace_value_for_na

write.csv(submit,file="lasso_information_gain.csv",row.names=F)
```














